---
title: "Series Preview"
date: today
params:
  away_team_id:  null
  home_team_id:  null
  series_label:  null
format:
  html:
    self-contained:   true
    embed-resources:  true
    theme:            cosmo
    toc:              true
    toc-depth:        2
    toc-title:        "Sections"
    toc-location:     left
    smooth-scroll:    true
execute:
  echo:    false
  warning: false
  message: false
---

```{r setup}
if (basename(getwd()) == "09_reporting") setwd("..")

library(dplyr)
library(gt)
library(baseballr)
library(httr)
library(jsonlite)

# ── Load pipeline cache ──────────────────────────────────────
cache_path <- "data/pipeline_cache.rds"
cache_ok   <- file.exists(cache_path) &&
              difftime(Sys.time(), file.mtime(cache_path), units = "hours") < 12
if (cache_ok) {
  cache <- readRDS(cache_path)
  list2env(cache, envir = .GlobalEnv)
  rm(cache)
} else {
  invisible(capture.output(source("run_pipeline_phase01.R")))
}

# ── Load helpers ─────────────────────────────────────────────
source("09_reporting/_deepdive_helpers.R")
source("09_reporting/_series_helpers.R")

# ── Series context ───────────────────────────────────────────
if (!exists("braves_series_context") || is.null(braves_series_context$next_series)) {
  stop("No upcoming series context found. Run the daily pipeline first.")
}

ns  <- braves_series_context$next_series
prb <- braves_series_context$next_series_probables

away_id   <- ns$away_team_id
home_id   <- ns$home_team_id
away_name <- ns$away_team_name
home_name <- ns$home_team_name
```

```{r nav-bar}
#| output: asis
scouting_file <- paste0("scouting_", format(Sys.Date(), "%Y-%m-%d"), ".html")

nav_html <- paste0(
  '<div style="margin-bottom:1.5rem;padding:10px 14px;background:#f8f9fa;',
  'border-radius:6px;border:1px solid #dee2e6;font-size:13px;">',
  '<a href="https://dpage02.github.io/mlb_scouting_report/" ',
  'style="color:#1a73e8;text-decoration:none;">\U0001f3e0 Home</a>',
  '&nbsp;&nbsp;|&nbsp;&nbsp;',
  '<a href="', scouting_file, '" style="color:#1a73e8;text-decoration:none;">',
  '\u2190 Today\'s Games</a>',
  '</div>'
)
cat(nav_html, "\n\n")
```

```{r series-header}
#| output: asis
cat(make_series_header_html(ns), "\n\n")
```

---

## Season at a Glance

*Current standings, run environment, and team-level offensive and pitching ratings.*

```{r team-overview}
#| output: asis
tbl <- make_series_team_overview_gt(away_id, home_id)
cat(gt::as_raw_html(tbl), "\n\n")
```

---

## Standings

*Both teams' divisional standings. Series participants highlighted.*

```{r standings}
#| output: asis
cat(make_series_standings_html(away_id, home_id), "\n\n")
```

---

## Ballpark & Conditions

```{r ballpark}
#| output: asis
# Use the first game of the series for venue + weather lookup
first_gpk <- ns$game_pks[1]

# Temporarily build a minimal game_context row for the helper
# if the series game isn't in today's game_context
if (exists("game_context") && first_gpk %in% game_context$game_pk) {
  bc_html <- tryCatch(make_ballpark_conditions_html(first_gpk), error = function(e) "")
} else {
  # Fallback: build directly from park_factors by home team
  pf_row <- if (exists("park_factors"))
    park_factors %>% dplyr::filter(mlbam_team_id == home_id) else dplyr::tibble()
  pf_runs <- if (nrow(pf_row) > 0) pf_row$pf_runs[1] else NA_real_
  pf_label <- if (is.na(pf_runs)) "N/A" else
    if (pf_runs >= 1.06) "Strong Hitter's Park" else
    if (pf_runs >= 1.02) "Hitter-Friendly" else
    if (pf_runs >= 0.98) "Neutral" else "Pitcher-Friendly"
  pf_color <- if (is.na(pf_runs)) "#aaa" else
    if (pf_runs >= 1.06) "#c0392b" else
    if (pf_runs >= 1.02) "#e67e22" else
    if (pf_runs >= 0.98) "#7f8c8d" else "#2980b9"

  venue <- if (nrow(pf_row) > 0) pf_row$venue_name[1] else ns$venue_name
  bc_html <- paste0(
    '<div style="font-size:0.92rem;font-weight:700;color:#2c3e50;margin-bottom:10px;">',
    venue, '</div>',
    '<div style="display:flex;flex-wrap:wrap;gap:10px;">',
    '<div style="flex:0 0 auto;min-width:160px;padding:10px 14px;background:#f8f9fa;',
    'border:1px solid #dee2e6;border-radius:6px;text-align:center;">',
    '<div style="font-size:10px;text-transform:uppercase;color:#888;font-weight:600;margin-bottom:4px;">',
    'Park Factor (Runs)</div>',
    '<div style="font-size:1.25rem;font-weight:700;color:', pf_color, ';">',
    if (!is.na(pf_runs)) sprintf("%.3f", pf_runs) else "\u2014", '</div>',
    '<div style="font-size:11px;color:', pf_color, ';font-weight:600;margin-top:3px;">',
    pf_label, '</div></div>',
    '<div style="flex:0 0 auto;padding:10px 14px;background:#fff8e7;border:1px solid #f0d08a;',
    'border-radius:6px;font-size:12px;color:#7d5a00;max-width:320px;align-self:center;">',
    '<strong>Note:</strong> Weather forecast not yet available for this series date.</div>',
    '</div>'
  )
}

if (nchar(bc_html) > 0) cat(bc_html, "\n\n")
```

---

## Probable Starters

*Tier-1: official MLB API probables. Shows TBD when not yet posted.*

```{r rotation}
#| output: asis
tbl <- make_series_rotation_gt(ns, prb)
cat(gt::as_raw_html(tbl), "\n\n")
```

---

## Pitch Arsenal

*Top pitches per probable starter — usage, velocity, and whiff rate.*

```{r arsenal}
#| output: asis
cat(make_series_arsenal_html(prb), "\n\n")
```

---

## Offense — `r away_name`

*Full roster: starters (top 9 PA) and bench (≥ 25 PA). 2026 season.*

```{r batting-away}
#| output: asis
opp_sp_away <- if (!is.null(prb) && nrow(prb) > 0 && !is.na(prb$home_pitcher_name[1]))
  prb$home_pitcher_name[1] else NULL
tbl <- make_series_batting_gt(away_id, opp_sp_name = opp_sp_away)
cat(gt::as_raw_html(tbl), "\n\n")
```

---

## Offense — `r home_name`

*Full roster: starters (top 9 PA) and bench (≥ 25 PA). 2026 season.*

```{r batting-home}
#| output: asis
opp_sp_home <- if (!is.null(prb) && nrow(prb) > 0 && !is.na(prb$away_pitcher_name[1]))
  prb$away_pitcher_name[1] else NULL
tbl <- make_series_batting_gt(home_id, opp_sp_name = opp_sp_home)
cat(gt::as_raw_html(tbl), "\n\n")
```

---

## Bullpen — `r away_name`

*Relief corps season stats (min. 5 IP), sorted by ERA.*

```{r bullpen-away}
#| output: asis
tbl <- make_series_bullpen_gt(away_id)
cat(gt::as_raw_html(tbl), "\n\n")
```

---

## Bullpen — `r home_name`

*Relief corps season stats (min. 5 IP), sorted by ERA.*

```{r bullpen-home}
#| output: asis
tbl <- make_series_bullpen_gt(home_id)
cat(gt::as_raw_html(tbl), "\n\n")
```
