---
title: "Pitcher Matchup"
date: today
params:
  game_pk: null
  game_date: null
format:
  html:
    self-contained: true
    embed-resources: true
    theme: cosmo
    toc: false
    smooth-scroll: true
execute:
  echo: false
  warning: false
  message: false
---

```{r setup}
#| output: false
if (basename(getwd()) == "09_reporting") setwd("..")

library(gt)
library(dplyr)

cache_path <- "data/pipeline_cache.rds"
cache_ok   <- file.exists(cache_path) &&
              difftime(Sys.time(), file.mtime(cache_path), units = "hours") < 12

if (cache_ok) {
  cache <- readRDS(cache_path)
  list2env(cache, envir = .GlobalEnv)
  rm(cache)
}

source("09_reporting/_report_helpers.R")
source("09_reporting/_deepdive_helpers.R")
source("09_reporting/_game_narrative_helpers.R")

gpk  <- as.integer(params$game_pk)
game <- game_context %>% dplyr::filter(game_pk == gpk)

away_team <- game$away_team_name
home_team <- game$home_team_name
matchup   <- sprintf("%s @ %s", away_team, home_team)
```

```{r header}
#| output: asis
cat(sprintf("# %s \u2014 Pitcher Matchup\n\n", matchup))
cat(paste0(
  "> **", format(as.Date(params$game_date), "%A, %B %d, %Y"), "**",
  " · ", game$venue_name, "\n\n"
))
```

```{r nav-bar}
#| output: asis
scouting_file <- paste0("scouting_", params$game_date, ".html")

away_abbr_str <- tryCatch({
  team_ids %>% dplyr::filter(mlbam_team_id == game$away_team_id) %>%
    dplyr::pull(team_abbr) %>% dplyr::first()
}, error = function(e) "AWAY")
home_abbr_str <- tryCatch({
  team_ids %>% dplyr::filter(mlbam_team_id == game$home_team_id) %>%
    dplyr::pull(team_abbr) %>% dplyr::first()
}, error = function(e) "HOME")
away_abbr_str <- if (length(away_abbr_str) == 0 || is.na(away_abbr_str)) "AWAY" else away_abbr_str
home_abbr_str <- if (length(home_abbr_str) == 0 || is.na(home_abbr_str)) "HOME" else home_abbr_str

deepdive_file  <- paste0("deepdive_",    params$game_date, "_", away_abbr_str, "_", home_abbr_str, ".html")
prediction_file <- paste0("prediction_", params$game_date, "_", away_abbr_str, "_", home_abbr_str, ".html")

cat(paste0(
  '<div style="margin-bottom:1.5rem; padding:10px 14px; background:#f8f9fa; ',
  'border-radius:6px; border:1px solid #dee2e6; font-size:13px;">',
  '<a href="', scouting_file, '" style="color:#1a73e8; text-decoration:none;">',
  '\u2190 Today\'s Games</a>',
  '&nbsp;&nbsp;|&nbsp;&nbsp;',
  '<a href="', deepdive_file, '" style="color:#1a73e8; text-decoration:none; font-weight:600;">',
  'Deep Dive</a>',
  '&nbsp;&nbsp;|&nbsp;&nbsp;',
  '<a href="', prediction_file, '" style="color:#1a73e8; text-decoration:none; font-weight:600;">',
  '\u26a1 Prediction</a>',
  '</div>'
), "\n\n")
```

---

## SP Arsenal

*Pitch mix, velocity, movement, and outcomes for today's starters. Sorted by usage.*

```{r arsenal}
#| output: asis
arsenal_tbl <- tryCatch(make_arsenal_gt(gpk), error = function(e) NULL)
if (!is.null(arsenal_tbl)) {
  cat(gt::as_raw_html(arsenal_tbl))
} else {
  cat("*Pitch arsenal data not available.*\n\n")
}
```

---

## Batter vs. SP Handedness

*How each lineup fares against today's opposing starter's arm side. Badges: 🔥 hot bat (last-7 OPS ≥ .900) · ⚡ 5+ game hit streak · ❄ cold bat.*

```{r pitcher-matchup}
#| output: asis
pm_html <- tryCatch(make_pitcher_matchup_html(gpk), error = function(e) {
  paste0('<p style="color:#888; font-style:italic;">Pitcher matchup unavailable: ',
         conditionMessage(e), '</p>')
})
cat(pm_html, "\n\n")
```

---

## Batter vs. Pitch Type

*Career stats (last 3 seasons, weighted by PA) for each lineup batter against the specific pitches today's starter throws. Select a pitch type to see the full breakdown.*

```{r batter-vs-pitch}
#| output: asis
bvp_html <- tryCatch(make_batter_vs_pitch_html(gpk), error = function(e) {
  paste0('<p style="color:#888; font-style:italic;">Batter vs. pitch type unavailable: ',
         conditionMessage(e), '</p>')
})
cat(bvp_html, "\n\n")
```
