---
title: "Team Deep Dive"
date: today
page-layout: full
params:
  game_pk: null
  side: null
  game_date: null
format:
  html:
    self-contained: true
    embed-resources: true
    theme: cosmo
    toc: true
    toc-depth: 3
    toc-title: "Sections"
    toc-location: left
    smooth-scroll: true
execute:
  echo: false
  warning: false
  message: false
---

```{=html}
<style>
/*
 * gt tables emit their own inline overflow-y:auto on the wrapping
 * .gt_table_container div. With height:auto that's normally a no-op, but
 * nested inside this page's flex/tab layout it can create an unwanted
 * nested vertical scroll region instead of letting the page scroll
 * normally. Same fix already applied to mlb_print.qmd and
 * mlb_game_deepdive.qmd for the same underlying gt behavior.
 */
.gt_table_container {
  overflow-y: visible !important;
}
</style>
```

```{r setup}
#| output: false
if (basename(getwd()) == "09_reporting") setwd("..")

library(gt)
library(dplyr)
library(stringr)

# Load from pipeline cache when available and fresh (written by run_all.R or
# a prior render today). Falls back to running the full pipeline if stale/missing.
cache_path <- "data/pipeline_cache.rds"
cache_ok   <- file.exists(cache_path) &&
              difftime(Sys.time(), file.mtime(cache_path), units = "hours") < 12

if (cache_ok) {
  cache <- readRDS(cache_path)
  list2env(cache, envir = .GlobalEnv)
  rm(cache)
} else {
  invisible(capture.output(source("run_pipeline_phase01.R")))
  pipeline_cache_objects <- c(
    "target_date", "target_season", "team_ids",
    "game_context", "lineup_context", "starter_matchup", "bullpen_grid",
    "offense_master_season", "player_career_offense", "player_career_pitching",
    "pitching_master_season", "pitcher_arsenal",
    "defense_master_season", "lineup_context_splits", "starter_splits",
    "player_season_fg_pitching", "player_season_mlb_pitching",
    "player_master_ids",
    "depth_charts"
  )
  pipeline_cache <- mget(
    pipeline_cache_objects[pipeline_cache_objects %in% ls()],
    envir = .GlobalEnv
  )
  saveRDS(pipeline_cache, cache_path)
}

source("09_reporting/_report_helpers.R")
source("09_reporting/_deepdive_helpers.R")

# Scope to this game and side
gpk      <- as.integer(params$game_pk)
side_val <- params$side
game     <- game_context %>% dplyr::filter(game_pk == gpk)

team_name <- if (side_val == "home") game$home_team_name else game$away_team_name
team_abbr <- if (side_val == "home") {
  dplyr::coalesce(
    team_ids %>% dplyr::filter(mlbam_team_id == game$home_team_id) %>%
      dplyr::pull(team_abbr) %>% dplyr::first(),
    "HOME"
  )
} else {
  dplyr::coalesce(
    team_ids %>% dplyr::filter(mlbam_team_id == game$away_team_id) %>%
      dplyr::pull(team_abbr) %>% dplyr::first(),
    "AWAY"
  )
}
opp_name <- if (side_val == "home") game$away_team_name else game$home_team_name

# Build navigation file references
report_date <- as.character(params$game_date)

away_abbr_nav <- tryCatch({
  team_ids %>% dplyr::filter(mlbam_team_id == game$away_team_id) %>%
    dplyr::pull(team_abbr) %>% dplyr::first()
}, error = function(e) as.character(game$away_team_id))

home_abbr_nav <- tryCatch({
  team_ids %>% dplyr::filter(mlbam_team_id == game$home_team_id) %>%
    dplyr::pull(team_abbr) %>% dplyr::first()
}, error = function(e) as.character(game$home_team_id))

away_abbr_nav <- dplyr::coalesce(away_abbr_nav, as.character(game$away_team_id))
home_abbr_nav <- dplyr::coalesce(home_abbr_nav, as.character(game$home_team_id))

# "" for a normal single game, "_G1"/"_G2" on a doubleheader day.
suffix_str <- dplyr::coalesce(game$file_suffix[1], "")

game_file     <- paste0("deepdive_", report_date, "_", away_abbr_nav, "_", home_abbr_nav, suffix_str, ".html")
scouting_file <- paste0("scouting_", report_date, ".html")
```

```{r header}
#| output: asis
cat(sprintf("# %s — Team Deep Dive\n\n", team_name))
cat(sprintf("> **%s** · %s @ %s · %s\n\n",
    format(as.Date(params$game_date), "%A, %B %d, %Y"),
    if (side_val == "away") team_name else opp_name,
    if (side_val == "home") team_name else opp_name,
    game$venue_name))
```

```{r nav-bar}
#| output: asis
cat(sprintf(
  '<div style="margin-bottom:1.5rem; padding:10px 14px; background:#f8f9fa; border-radius:6px; border:1px solid #dee2e6; font-size:13px;">
  <a href="%s" style="color:#1a73e8; text-decoration:none;">← Today\'s Games</a>
  &nbsp;·&nbsp;
  <a href="%s" style="color:#1a73e8; text-decoration:none;">Game: %s @ %s</a>
</div>\n\n',
  scouting_file,
  game_file,
  away_abbr_nav,
  home_abbr_nav
))
```

---

## Full Breakdown

*4-pillar tabset (Master Build Spec §3): Offense, Baserunning, Defense, and Catcher —
the same shared research module referenced from both the Series Preview and the
Game Day Preview.*

```{r pillar-tab-helpers, include=FALSE}
# Two independent pandoc/CommonMark quirks corrupt fenced-div (panel-tabset)
# parsing when a gt table is emitted inside one, unless both are fixed:
# 1. gt::as_raw_html() sometimes emits TWO consecutive whitespace-only lines
#    (e.g. around an empty tfoot). A blank line inside a raw HTML block ends
#    it early under CommonMark's rules; {2,} collapses runs of any length,
#    not just one (a single-pass regex only catching one blank line at a
#    time misses runs of 2+, since gsub doesn't backtrack/overlap matches).
# 2. gt emits bare `<col style="...">` tags (HTML void elements) for column
#    widths. Pandoc's block-tag matcher doesn't recognize <col> as
#    self-closing and treats it as an unterminated open tag, silently
#    swallowing everything through EOF into one Div (including this
#    tabset's own closing ':::', which then leaks into the page as literal
#    text). Self-closing the tag (`<col ... />`) fixes it.
# Same helper as mlb_game_deepdive.qmd's Full Breakdown section.
.gt_html <- function(tbl) {
  html <- gt::as_raw_html(tbl)
  html <- gsub("(\n[ \t]*){2,}", "\n", html)
  gsub("<col([^>]*)>", "<col\\1 />", html)
}

# Combines Batter Intelligence (Overview / Discipline & Contact / Batted Ball),
# Sustainability, and Clutch+Platoon into one Offense tab, stacked as a
# narrative sequence (approach -> contact -> quality -> deserved outcomes ->
# clutch -> platoon) rather than further nested tabs.
.render_offense_tab <- function(gpk, side) {
  sub_hdr <- function(txt) sprintf(
    '<div style="font-size:0.85rem;font-weight:700;color:#2c3e50;margin:1.1rem 0 0.4rem 0;text-transform:uppercase;letter-spacing:0.02em;">%s</div>',
    txt
  )

  bi <- tryCatch(make_batter_intelligence_gt(gpk, side), error = function(e) list())
  if (length(bi) > 0) {
    cat(sub_hdr("Production &amp; Approach"), "\n\n")
    cat(.gt_html(bi[["Overview"]]), "\n\n")
    cat(sub_hdr("Plate Discipline, Contact &amp; Quality of Contact"), "\n\n")
    cat(.gt_html(bi[["Discipline & Contact"]]), "\n\n")
    cat(sub_hdr("Batted Ball Profile"), "\n\n")
    cat(.gt_html(bi[["Batted Ball & Profile"]]), "\n\n")
  } else {
    cat('<p style="color:#888;font-style:italic;">Batter intelligence data not available.</p>\n\n')
  }

  sust <- tryCatch(make_sustainability_gt(gpk, side), error = function(e) NULL)
  if (!is.null(sust)) {
    cat(sub_hdr("Deserved Outcomes (Sustainability)"), "\n\n")
    cat(.gt_html(sust), "\n\n")
  }

  cp <- tryCatch(make_offense_clutch_platoon_gt(gpk, side), error = function(e) list())
  if (length(cp) > 0) {
    cat(sub_hdr("Clutch / Leverage"), "\n\n")
    cat(.gt_html(cp[["Clutch / Leverage"]]), "\n\n")
    cat(sub_hdr("Handedness Split (Season-Long)"), "\n\n")
    cat(.gt_html(cp[["Handedness Split"]]), "\n\n")
  }
}

.render_baserunning_tab <- function(gpk, side) {
  tbl <- tryCatch(make_baserunning_gt(gpk, side), error = function(e) NULL)
  if (!is.null(tbl)) cat(.gt_html(tbl), "\n\n")
  else cat('<p style="color:#888;font-style:italic;">Baserunning data not available.</p>\n\n')
}

.render_defense_tab <- function(gpk, side) {
  tbl <- tryCatch(make_lineup_defense_gt(gpk, side), error = function(e) NULL)
  if (!is.null(tbl)) cat(.gt_html(tbl), "\n\n")
  else cat('<p style="color:#888;font-style:italic;">Defense data not available.</p>\n\n')
}

# Position-gated: only emits content (and thus only becomes a meaningful
# tab) when this team's lineup has a catcher; make_catcher_defense_gt
# returns NULL otherwise.
.render_catcher_tab <- function(gpk, side) {
  tbl <- tryCatch(make_catcher_defense_gt(gpk, side), error = function(e) NULL)
  if (!is.null(tbl)) cat(.gt_html(tbl), "\n\n")
  else cat('<p style="color:#888;font-style:italic;">No catcher in this lineup.</p>\n\n')
}
```

::: {.panel-tabset}

### Offense

```{r offense-tab}
#| output: asis
.render_offense_tab(gpk, side_val)
```

### Baserunning

```{r baserunning-tab}
#| output: asis
.render_baserunning_tab(gpk, side_val)
```

### Defense

```{r defense-tab}
#| output: asis
.render_defense_tab(gpk, side_val)
```

### Catcher

```{r catcher-tab}
#| output: asis
.render_catcher_tab(gpk, side_val)
```

:::

---

## Lineup — Season in Context

*Shows current season vs prior season vs career average for each player in today's lineup.*

```{r lineup-context}
#| output: asis
if (exists("make_season_context_gt")) {
  context_tbl <- make_season_context_gt(gpk, side_val)
  if (!is.null(context_tbl)) cat(gt::as_raw_html(context_tbl))
} else {
  cat('<div style="padding:20px; background:#fff3cd; border:1px solid #ffc107; border-radius:6px; color:#856404; font-size:14px; margin:1rem 0;">
  <strong>&#9888; Coming Soon</strong> — Season-in-context table (current vs prior season vs career) will appear here once implemented.
</div>\n\n')
}
```

---

## Career History

*Last 5 seasons + current season, totals aggregated across teams.*

```{r career-offense}
#| output: asis
cat(gt::as_raw_html(make_career_offense_gt(gpk, side_val)))
```

---

## Pitching — Projected Rotation

*SP1–SP5 from FanGraphs depth chart with full season stats.*

```{r rotation}
#| output: asis
rot_tbl <- make_rotation_gt(gpk, side_val)
if (!is.null(rot_tbl)) {
  cat(gt::as_raw_html(rot_tbl))
} else {
  cat('<p style="color:#888; font-size:13px; font-style:italic;">Rotation data not available — depth chart may not have loaded.</p>\n\n')
}
```

---

## Pitching — Bullpen Deep Dive

*Full season stats for all available bullpen arms.*

```{r bullpen-deep}
#| output: asis
if (exists("make_bullpen_deep_gt")) {
  bp_deep <- make_bullpen_deep_gt(gpk, side_val)
  if (!is.null(bp_deep)) cat(gt::as_raw_html(bp_deep))
} else {
  cat('<div style="padding:20px; background:#fff3cd; border:1px solid #ffc107; border-radius:6px; color:#856404; font-size:14px; margin:1rem 0;">
  <strong>&#9888; Coming Soon</strong> — Full bullpen season stats (ERA, FIP, K%, BB%, WHIP, leverage) will appear here once implemented.
</div>\n\n')
}
```

---

## Pitching — Bullpen Arsenal

*Pitch mix and characteristics for each bullpen arm.*

```{r bullpen-arsenal}
#| output: asis
if (exists("make_bullpen_arsenal_gt")) {
  bp_arsenal <- make_bullpen_arsenal_gt(gpk, side_val)
  if (!is.null(bp_arsenal)) cat(gt::as_raw_html(bp_arsenal))
} else {
  cat('<div style="padding:20px; background:#fff3cd; border:1px solid #ffc107; border-radius:6px; color:#856404; font-size:14px; margin:1rem 0;">
  <strong>&#9888; Coming Soon</strong> — Bullpen pitch arsenal (pitch types, velocity, usage%, spin rate, movement) will appear here once Statcast bullpen data is integrated.
</div>\n\n')
}
```
