---
title: "Batter Intelligence"
date: today
params:
  game_pk: null
  game_date: null
format:
  html:
    self-contained: true
    embed-resources: true
    theme: cosmo
    toc: false
    smooth-scroll: true
execute:
  echo: false
  warning: false
  message: false
---

```{r setup}
#| output: false
if (basename(getwd()) == "09_reporting") setwd("..")

library(gt)
library(dplyr)

cache_path <- "data/pipeline_cache.rds"
cache_ok   <- file.exists(cache_path) &&
              difftime(Sys.time(), file.mtime(cache_path), units = "hours") < 12

if (cache_ok) {
  cache <- readRDS(cache_path)
  list2env(cache, envir = .GlobalEnv)
  rm(cache)
}

source("09_reporting/_report_helpers.R")
source("09_reporting/_deepdive_helpers.R")
source("09_reporting/_game_narrative_helpers.R")

gpk  <- as.integer(params$game_pk)
game <- game_context %>% dplyr::filter(game_pk == gpk)

away_team <- game$away_team_name
home_team <- game$home_team_name
matchup   <- sprintf("%s @ %s", away_team, home_team)

# Resolve opposing SP names for section headers
away_sp_name <- tryCatch({
  r <- starter_matchup %>% dplyr::filter(game_pk == gpk, side == "away")
  if (nrow(r) > 0) dplyr::coalesce(r$pitcher_name[1], "Away SP") else "Away SP"
}, error = function(e) "Away SP")

home_sp_name <- tryCatch({
  r <- starter_matchup %>% dplyr::filter(game_pk == gpk, side == "home")
  if (nrow(r) > 0) dplyr::coalesce(r$pitcher_name[1], "Home SP") else "Home SP"
}, error = function(e) "Home SP")
```

```{r header}
#| output: asis
cat(sprintf("# %s \u2014 Batter Intelligence\n\n", matchup))
cat(paste0(
  "> **", format(as.Date(params$game_date), "%A, %B %d, %Y"), "**",
  " \u00b7 ", game$venue_name, "\n\n"
))
```

```{r nav-bar}
#| output: asis
scouting_file <- paste0("scouting_", params$game_date, ".html")

away_abbr_str <- tryCatch({
  team_ids %>% dplyr::filter(mlbam_team_id == game$away_team_id) %>%
    dplyr::pull(team_abbr) %>% dplyr::first()
}, error = function(e) "AWAY")
home_abbr_str <- tryCatch({
  team_ids %>% dplyr::filter(mlbam_team_id == game$home_team_id) %>%
    dplyr::pull(team_abbr) %>% dplyr::first()
}, error = function(e) "HOME")
away_abbr_str <- if (length(away_abbr_str) == 0 || is.na(away_abbr_str)) "AWAY" else away_abbr_str
home_abbr_str <- if (length(home_abbr_str) == 0 || is.na(home_abbr_str)) "HOME" else home_abbr_str

# "" for a normal single game, "_G1"/"_G2" on a doubleheader day.
suffix_str <- dplyr::coalesce(game$file_suffix[1], "")

deepdive_file   <- paste0("deepdive_",   params$game_date, "_", away_abbr_str, "_", home_abbr_str, suffix_str, ".html")
breakdown_file  <- paste0("breakdown_",  params$game_date, "_", away_abbr_str, "_", home_abbr_str, suffix_str, ".html")
matchup_file    <- paste0("matchup_",    params$game_date, "_", away_abbr_str, "_", home_abbr_str, suffix_str, ".html")
prediction_file <- paste0("prediction_", params$game_date, "_", away_abbr_str, "_", home_abbr_str, suffix_str, ".html")

cat(paste0(
  '<div style="margin-bottom:1.5rem; padding:10px 14px; background:#f8f9fa; ',
  'border-radius:6px; border:1px solid #dee2e6; font-size:13px;">',
  '<a href="', scouting_file, '" style="color:#1a73e8; text-decoration:none;">',
  '\u2190 Today\'s Games</a>',
  '&nbsp;&nbsp;|&nbsp;&nbsp;',
  '<a href="', deepdive_file, '" style="color:#1a73e8; text-decoration:none; font-weight:600;">',
  'Deep Dive</a>',
  '&nbsp;&nbsp;|&nbsp;&nbsp;',
  '<a href="', breakdown_file, '" style="color:#1a73e8; text-decoration:none; font-weight:600;">',
  '\U0001f4ca Full Breakdown</a>',
  '&nbsp;&nbsp;|&nbsp;&nbsp;',
  '<a href="', matchup_file, '" style="color:#1a73e8; text-decoration:none; font-weight:600;">',
  '\u26be Pitcher Matchup</a>',
  '&nbsp;&nbsp;|&nbsp;&nbsp;',
  '<a href="', prediction_file, '" style="color:#1a73e8; text-decoration:none; font-weight:600;">',
  '\u26a1 Prediction</a>',
  '</div>'
), "\n\n")
```

---

## Lineup Overview

*PA-weighted team offensive identity — quality, approach, power, and contact quality at a glance.*

```{r lineup-overview}
#| output: asis
overview_html <- tryCatch(make_lineup_overview_html(gpk), error = function(e) {
  paste0('<p style="color:#888; font-style:italic;">Lineup overview unavailable: ',
         conditionMessage(e), '</p>')
})
cat(overview_html, "\n\n")
```

---

## vs Tonight's Arsenal

*Run value per 100 pitches faced — positive = above average vs that pitch type.*

### `r away_team` batters vs `r home_sp_name`

```{r pitch-vuln-away}
#| output: asis
vuln_away <- tryCatch(make_pitch_vulnerability_gt(gpk, "away"), error = function(e) {
  dplyr::tibble(Note = paste0("Unavailable: ", conditionMessage(e))) %>%
    gt::gt() %>%
    gt::tab_header(title = paste0(away_team, " vs Tonight's Arsenal")) %>%
    gt::tab_options(table.font.size = 12, heading.align = "left",
                    data_row.padding = gt::px(4)) %>%
    gt::opt_stylize(style = 1, color = "blue")
})
cat(gt::as_raw_html(vuln_away), "\n\n")
```

### `r home_team` batters vs `r away_sp_name`

```{r pitch-vuln-home}
#| output: asis
vuln_home <- tryCatch(make_pitch_vulnerability_gt(gpk, "home"), error = function(e) {
  dplyr::tibble(Note = paste0("Unavailable: ", conditionMessage(e))) %>%
    gt::gt() %>%
    gt::tab_header(title = paste0(home_team, " vs Tonight's Arsenal")) %>%
    gt::tab_options(table.font.size = 12, heading.align = "left",
                    data_row.padding = gt::px(4)) %>%
    gt::opt_stylize(style = 1, color = "blue")
})
cat(gt::as_raw_html(vuln_home), "\n\n")
```

---

## Full Batter Breakdown

*Batter Intelligence (production, plate discipline, contact quality, batted*
*ball profile), Sustainability (expected vs. actual outcomes), and Baserunning*
*for both lineups now live on the Full Breakdown page — one shared copy*
*instead of duplicating the same tables here.*

```{r full-breakdown-link}
#| output: asis
cat(sprintf(
  '<a href="%s" style="display:inline-block;background:#1a73e8;color:white;font-weight:600;padding:8px 16px;border-radius:6px;text-decoration:none;">📊 Open Full Breakdown →</a>',
  breakdown_file
), "\n\n")
cat('<p style="color:#888;font-size:0.85rem;margin-top:8px;">Opens on the Lineup tab, ',
    away_team, ' Offense sub-tab shown first — switch tabs there for ',
    home_team, ', Baserunning, Defense, or Catcher.</p>\n\n', sep = "")
```
