---
title: "Lineup Analysis"
date: today
params:
  game_pk: null
  game_date: null
format:
  html:
    self-contained: true
    embed-resources: true
    theme: cosmo
    toc: false
    smooth-scroll: true
execute:
  echo: false
  warning: false
  message: false
---

```{r setup}
#| output: false
if (basename(getwd()) == "09_reporting") setwd("..")

library(gt)
library(dplyr)

cache_path <- "data/pipeline_cache.rds"
cache_ok   <- file.exists(cache_path) &&
              difftime(Sys.time(), file.mtime(cache_path), units = "hours") < 12

if (cache_ok) {
  cache <- readRDS(cache_path)
  list2env(cache, envir = .GlobalEnv)
  rm(cache)
}

source("09_reporting/_report_helpers.R")
source("09_reporting/_deepdive_helpers.R")
source("09_reporting/_game_narrative_helpers.R")

gpk  <- as.integer(params$game_pk)
game <- game_context %>% dplyr::filter(game_pk == gpk)

away_team <- game$away_team_name
home_team <- game$home_team_name
matchup   <- sprintf("%s @ %s", away_team, home_team)
```

```{r header}
#| output: asis
cat(sprintf("# %s \u2014 Lineup Analysis\n\n", matchup))
cat(paste0(
  "> **", format(as.Date(params$game_date), "%A, %B %d, %Y"), "**",
  " · ", game$venue_name, "\n\n"
))
```

```{r nav-bar}
#| output: asis
scouting_file <- paste0("scouting_", params$game_date, ".html")

away_abbr_str <- tryCatch({
  team_ids %>% dplyr::filter(mlbam_team_id == game$away_team_id) %>%
    dplyr::pull(team_abbr) %>% dplyr::first()
}, error = function(e) "AWAY")
home_abbr_str <- tryCatch({
  team_ids %>% dplyr::filter(mlbam_team_id == game$home_team_id) %>%
    dplyr::pull(team_abbr) %>% dplyr::first()
}, error = function(e) "HOME")
away_abbr_str <- if (length(away_abbr_str) == 0 || is.na(away_abbr_str)) "AWAY" else away_abbr_str
home_abbr_str <- if (length(home_abbr_str) == 0 || is.na(home_abbr_str)) "HOME" else home_abbr_str

deepdive_file   <- paste0("deepdive_",   params$game_date, "_", away_abbr_str, "_", home_abbr_str, ".html")
matchup_file    <- paste0("matchup_",    params$game_date, "_", away_abbr_str, "_", home_abbr_str, ".html")
prediction_file <- paste0("prediction_", params$game_date, "_", away_abbr_str, "_", home_abbr_str, ".html")

cat(paste0(
  '<div style="margin-bottom:1.5rem; padding:10px 14px; background:#f8f9fa; ',
  'border-radius:6px; border:1px solid #dee2e6; font-size:13px;">',
  '<a href="', scouting_file, '" style="color:#1a73e8; text-decoration:none;">',
  '\u2190 Today\'s Games</a>',
  '&nbsp;&nbsp;|&nbsp;&nbsp;',
  '<a href="', deepdive_file, '" style="color:#1a73e8; text-decoration:none; font-weight:600;">',
  'Deep Dive</a>',
  '&nbsp;&nbsp;|&nbsp;&nbsp;',
  '<a href="', matchup_file, '" style="color:#1a73e8; text-decoration:none; font-weight:600;">',
  '\u26be Pitcher Matchup</a>',
  '&nbsp;&nbsp;|&nbsp;&nbsp;',
  '<a href="', prediction_file, '" style="color:#1a73e8; text-decoration:none; font-weight:600;">',
  '\u26a1 Prediction</a>',
  '</div>'
), "\n\n")
```

---

## Lineup Projections

*Steamer true-talent wRC+ vs current season stats. wRC+ color scale: 130+ elite, 115–129 above average, 100–114 average, 85–99 below average, <85 weak.*

```{r lineup-projections}
#| output: asis
proj_html <- tryCatch(make_lineup_projection_html(gpk), error = function(e) {
  paste0('<p style="color:#888; font-style:italic;">Lineup projections unavailable: ',
         conditionMessage(e), '</p>')
})
cat(proj_html, "\n\n")
```

---

## Analytical Breakdown

*Current season stats from MLB API, FanGraphs (all leaderboard types), and Statcast. Each section focuses on a different dimension of hitting.*

### `r away_team`

```{r lineup-away-full}
#| output: asis
tables_away <- tryCatch(make_lineup_full_gt(gpk, "away"), error = function(e) NULL)
if (!is.null(tables_away)) {
  for (nm in names(tables_away)) {
    cat(sprintf('\n\n<h4 style="margin-top:1.4rem; margin-bottom:0.3rem; color:#2c3e50;">%s</h4>\n\n', nm))
    cat(gt::as_raw_html(tables_away[[nm]]))
    cat("\n\n")
  }
} else {
  cat("*Analytical breakdown not available for ", away_team, ".*\n\n")
}
```

### `r home_team`

```{r lineup-home-full}
#| output: asis
tables_home <- tryCatch(make_lineup_full_gt(gpk, "home"), error = function(e) NULL)
if (!is.null(tables_home)) {
  for (nm in names(tables_home)) {
    cat(sprintf('\n\n<h4 style="margin-top:1.4rem; margin-bottom:0.3rem; color:#2c3e50;">%s</h4>\n\n', nm))
    cat(gt::as_raw_html(tables_home[[nm]]))
    cat("\n\n")
  }
} else {
  cat("*Analytical breakdown not available for ", home_team, ".*\n\n")
}
```

---

## Career History

*Last 5 seasons + current season, totals aggregated across teams.*

### `r away_team`

```{r career-away}
#| output: asis
career_away <- tryCatch(make_career_offense_gt(gpk, "away"), error = function(e) NULL)
if (!is.null(career_away)) {
  cat(gt::as_raw_html(career_away))
} else {
  cat("*Career history not available for ", away_team, ".*\n\n")
}
```

### `r home_team`

```{r career-home}
#| output: asis
career_home <- tryCatch(make_career_offense_gt(gpk, "home"), error = function(e) NULL)
if (!is.null(career_home)) {
  cat(gt::as_raw_html(career_home))
} else {
  cat("*Career history not available for ", home_team, ".*\n\n")
}
```

---

## Matchup Splits

*How each lineup fares vs today's opposing starter's arm side.*

### `r away_team`

```{r splits-away}
#| output: asis
splits_away <- tryCatch(make_lineup_splits_gt(gpk, "away"), error = function(e) NULL)
if (!is.null(splits_away)) {
  cat(gt::as_raw_html(splits_away))
} else {
  cat("*Matchup splits not available for ", away_team, ".*\n\n")
}
```

### `r home_team`

```{r splits-home}
#| output: asis
splits_home <- tryCatch(make_lineup_splits_gt(gpk, "home"), error = function(e) NULL)
if (!is.null(splits_home)) {
  cat(gt::as_raw_html(splits_home))
} else {
  cat("*Matchup splits not available for ", home_team, ".*\n\n")
}
```
