---
title: "Team Deep Dive"
date: today
params:
  game_pk: null
  side: null
  game_date: null
format:
  html:
    self-contained: true
    embed-resources: true
    theme: cosmo
    toc: true
    toc-depth: 3
    toc-title: "Sections"
    toc-location: left
    smooth-scroll: true
execute:
  echo: false
  warning: false
  message: false
---

```{r setup}
#| output: false
if (basename(getwd()) == "09_reporting") setwd("..")

library(gt)
library(dplyr)
library(stringr)

# Load from pipeline cache when available and fresh (written by run_all.R or
# a prior render today). Falls back to running the full pipeline if stale/missing.
cache_path <- "data/pipeline_cache.rds"
cache_ok   <- file.exists(cache_path) &&
              difftime(Sys.time(), file.mtime(cache_path), units = "hours") < 12

if (cache_ok) {
  cache <- readRDS(cache_path)
  list2env(cache, envir = .GlobalEnv)
  rm(cache)
} else {
  invisible(capture.output(source("run_pipeline_phase01.R")))
  pipeline_cache_objects <- c(
    "target_date", "target_season", "team_ids",
    "game_context", "lineup_context", "starter_matchup", "bullpen_grid",
    "offense_master_season", "player_career_offense", "player_career_pitching",
    "pitching_master_season", "pitcher_arsenal",
    "defense_master_season", "lineup_context_splits", "starter_splits",
    "player_season_fg_pitching", "player_season_mlb_pitching",
    "player_master_ids",
    "depth_charts"
  )
  pipeline_cache <- mget(
    pipeline_cache_objects[pipeline_cache_objects %in% ls()],
    envir = .GlobalEnv
  )
  saveRDS(pipeline_cache, cache_path)
}

source("09_reporting/_report_helpers.R")
source("09_reporting/_deepdive_helpers.R")

# Scope to this game and side
gpk      <- as.integer(params$game_pk)
side_val <- params$side
game     <- game_context %>% dplyr::filter(game_pk == gpk)

team_name <- if (side_val == "home") game$home_team_name else game$away_team_name
team_abbr <- if (side_val == "home") {
  dplyr::coalesce(
    team_ids %>% dplyr::filter(mlbam_team_id == game$home_team_id) %>%
      dplyr::pull(team_abbr) %>% dplyr::first(),
    "HOME"
  )
} else {
  dplyr::coalesce(
    team_ids %>% dplyr::filter(mlbam_team_id == game$away_team_id) %>%
      dplyr::pull(team_abbr) %>% dplyr::first(),
    "AWAY"
  )
}
opp_name <- if (side_val == "home") game$away_team_name else game$home_team_name

# Build navigation file references
report_date <- as.character(params$game_date)

away_abbr_nav <- tryCatch({
  team_ids %>% dplyr::filter(mlbam_team_id == game$away_team_id) %>%
    dplyr::pull(team_abbr) %>% dplyr::first()
}, error = function(e) as.character(game$away_team_id))

home_abbr_nav <- tryCatch({
  team_ids %>% dplyr::filter(mlbam_team_id == game$home_team_id) %>%
    dplyr::pull(team_abbr) %>% dplyr::first()
}, error = function(e) as.character(game$home_team_id))

away_abbr_nav <- dplyr::coalesce(away_abbr_nav, as.character(game$away_team_id))
home_abbr_nav <- dplyr::coalesce(home_abbr_nav, as.character(game$home_team_id))

game_file     <- paste0("deepdive_", report_date, "_", away_abbr_nav, "_", home_abbr_nav, ".html")
scouting_file <- paste0("scouting_", report_date, ".html")
```

```{r header}
#| output: asis
cat(sprintf("# %s — Team Deep Dive\n\n", team_name))
cat(sprintf("> **%s** · %s @ %s · %s\n\n",
    format(as.Date(params$game_date), "%A, %B %d, %Y"),
    if (side_val == "away") team_name else opp_name,
    if (side_val == "home") team_name else opp_name,
    game$venue_name))
```

```{r nav-bar}
#| output: asis
cat(sprintf(
  '<div style="margin-bottom:1.5rem; padding:10px 14px; background:#f8f9fa; border-radius:6px; border:1px solid #dee2e6; font-size:13px;">
  <a href="%s" style="color:#1a73e8; text-decoration:none;">← Today\'s Games</a>
  &nbsp;·&nbsp;
  <a href="%s" style="color:#1a73e8; text-decoration:none;">Game: %s @ %s</a>
</div>\n\n',
  scouting_file,
  game_file,
  away_abbr_nav,
  home_abbr_nav
))
```

---

## Lineup — Current Season

*Current season batting stats across all leaderboard dimensions for each player in today's lineup.*

```{r lineup-current}
#| output: asis
tables_side <- make_lineup_full_gt(gpk, side_val)
for (nm in names(tables_side)) {
  cat(sprintf('\n\n<h4 style="margin-top:1.4rem; margin-bottom:0.3rem; color:#2c3e50;">%s</h4>\n\n', nm))
  cat(gt::as_raw_html(tables_side[[nm]]))
  cat("\n\n")
}
```

---

## Lineup — Season in Context

*Shows current season vs prior season vs career average for each player in today's lineup.*

```{r lineup-context}
#| output: asis
if (exists("make_season_context_gt")) {
  context_tbl <- make_season_context_gt(gpk, side_val)
  if (!is.null(context_tbl)) cat(gt::as_raw_html(context_tbl))
} else {
  cat('<div style="padding:20px; background:#fff3cd; border:1px solid #ffc107; border-radius:6px; color:#856404; font-size:14px; margin:1rem 0;">
  <strong>&#9888; Coming Soon</strong> — Season-in-context table (current vs prior season vs career) will appear here once implemented.
</div>\n\n')
}
```

---

## Lineup — vs Expected Stats

*[Placeholder — coming soon]*

<div style="padding:20px; background:#fff3cd; border:1px solid #ffc107; border-radius:6px; color:#856404; font-size:14px; margin:1rem 0;">
  <strong>&#9888; Coming Soon</strong> — Expected vs actual stat comparison (xBA vs AVG, xwOBA vs wOBA, Barrel%) will appear here once historical Statcast data is integrated.
</div>

---

## Career History

*Last 5 seasons + current season, totals aggregated across teams.*

```{r career-offense}
#| output: asis
cat(gt::as_raw_html(make_career_offense_gt(gpk, side_val)))
```

---

## Pitching — Projected Rotation

*SP1–SP5 from FanGraphs depth chart with full season stats.*

```{r rotation}
#| output: asis
rot_tbl <- make_rotation_gt(gpk, side_val)
if (!is.null(rot_tbl)) {
  cat(gt::as_raw_html(rot_tbl))
} else {
  cat('<p style="color:#888; font-size:13px; font-style:italic;">Rotation data not available — depth chart may not have loaded.</p>\n\n')
}
```

---

## Pitching — Bullpen Deep Dive

*Full season stats for all available bullpen arms.*

```{r bullpen-deep}
#| output: asis
if (exists("make_bullpen_deep_gt")) {
  bp_deep <- make_bullpen_deep_gt(gpk, side_val)
  if (!is.null(bp_deep)) cat(gt::as_raw_html(bp_deep))
} else {
  cat('<div style="padding:20px; background:#fff3cd; border:1px solid #ffc107; border-radius:6px; color:#856404; font-size:14px; margin:1rem 0;">
  <strong>&#9888; Coming Soon</strong> — Full bullpen season stats (ERA, FIP, K%, BB%, WHIP, leverage) will appear here once implemented.
</div>\n\n')
}
```

---

## Pitching — Bullpen Arsenal

*Pitch mix and characteristics for each bullpen arm.*

```{r bullpen-arsenal}
#| output: asis
if (exists("make_bullpen_arsenal_gt")) {
  bp_arsenal <- make_bullpen_arsenal_gt(gpk, side_val)
  if (!is.null(bp_arsenal)) cat(gt::as_raw_html(bp_arsenal))
} else {
  cat('<div style="padding:20px; background:#fff3cd; border:1px solid #ffc107; border-radius:6px; color:#856404; font-size:14px; margin:1rem 0;">
  <strong>&#9888; Coming Soon</strong> — Bullpen pitch arsenal (pitch types, velocity, usage%, spin rate, movement) will appear here once Statcast bullpen data is integrated.
</div>\n\n')
}
```
