---
title: "Batter Intelligence"
date: today
params:
  game_pk: null
  game_date: null
format:
  html:
    self-contained: true
    embed-resources: true
    theme: cosmo
    toc: false
    smooth-scroll: true
execute:
  echo: false
  warning: false
  message: false
---

```{r setup}
#| output: false
if (basename(getwd()) == "09_reporting") setwd("..")

library(gt)
library(dplyr)

cache_path <- "data/pipeline_cache.rds"
cache_ok   <- file.exists(cache_path) &&
              difftime(Sys.time(), file.mtime(cache_path), units = "hours") < 12

if (cache_ok) {
  cache <- readRDS(cache_path)
  list2env(cache, envir = .GlobalEnv)
  rm(cache)
}

source("09_reporting/_report_helpers.R")
source("09_reporting/_deepdive_helpers.R")
source("09_reporting/_game_narrative_helpers.R")

gpk  <- as.integer(params$game_pk)
game <- game_context %>% dplyr::filter(game_pk == gpk)

away_team <- game$away_team_name
home_team <- game$home_team_name
matchup   <- sprintf("%s @ %s", away_team, home_team)

# Resolve opposing SP names for section headers
away_sp_name <- tryCatch({
  r <- starter_matchup %>% dplyr::filter(game_pk == gpk, side == "away")
  if (nrow(r) > 0) dplyr::coalesce(r$pitcher_name[1], "Away SP") else "Away SP"
}, error = function(e) "Away SP")

home_sp_name <- tryCatch({
  r <- starter_matchup %>% dplyr::filter(game_pk == gpk, side == "home")
  if (nrow(r) > 0) dplyr::coalesce(r$pitcher_name[1], "Home SP") else "Home SP"
}, error = function(e) "Home SP")
```

```{r header}
#| output: asis
cat(sprintf("# %s \u2014 Batter Intelligence\n\n", matchup))
cat(paste0(
  "> **", format(as.Date(params$game_date), "%A, %B %d, %Y"), "**",
  " \u00b7 ", game$venue_name, "\n\n"
))
```

```{r nav-bar}
#| output: asis
scouting_file <- paste0("scouting_", params$game_date, ".html")

away_abbr_str <- tryCatch({
  team_ids %>% dplyr::filter(mlbam_team_id == game$away_team_id) %>%
    dplyr::pull(team_abbr) %>% dplyr::first()
}, error = function(e) "AWAY")
home_abbr_str <- tryCatch({
  team_ids %>% dplyr::filter(mlbam_team_id == game$home_team_id) %>%
    dplyr::pull(team_abbr) %>% dplyr::first()
}, error = function(e) "HOME")
away_abbr_str <- if (length(away_abbr_str) == 0 || is.na(away_abbr_str)) "AWAY" else away_abbr_str
home_abbr_str <- if (length(home_abbr_str) == 0 || is.na(home_abbr_str)) "HOME" else home_abbr_str

deepdive_file   <- paste0("deepdive_",   params$game_date, "_", away_abbr_str, "_", home_abbr_str, ".html")
matchup_file    <- paste0("matchup_",    params$game_date, "_", away_abbr_str, "_", home_abbr_str, ".html")
prediction_file <- paste0("prediction_", params$game_date, "_", away_abbr_str, "_", home_abbr_str, ".html")

cat(paste0(
  '<div style="margin-bottom:1.5rem; padding:10px 14px; background:#f8f9fa; ',
  'border-radius:6px; border:1px solid #dee2e6; font-size:13px;">',
  '<a href="', scouting_file, '" style="color:#1a73e8; text-decoration:none;">',
  '\u2190 Today\'s Games</a>',
  '&nbsp;&nbsp;|&nbsp;&nbsp;',
  '<a href="', deepdive_file, '" style="color:#1a73e8; text-decoration:none; font-weight:600;">',
  'Deep Dive</a>',
  '&nbsp;&nbsp;|&nbsp;&nbsp;',
  '<a href="', matchup_file, '" style="color:#1a73e8; text-decoration:none; font-weight:600;">',
  '\u26be Pitcher Matchup</a>',
  '&nbsp;&nbsp;|&nbsp;&nbsp;',
  '<a href="', prediction_file, '" style="color:#1a73e8; text-decoration:none; font-weight:600;">',
  '\u26a1 Prediction</a>',
  '</div>'
), "\n\n")
```

---

## Lineup Overview

*PA-weighted team offensive identity — quality, approach, power, and contact quality at a glance.*

```{r lineup-overview}
#| output: asis
overview_html <- tryCatch(make_lineup_overview_html(gpk), error = function(e) {
  paste0('<p style="color:#888; font-style:italic;">Lineup overview unavailable: ',
         conditionMessage(e), '</p>')
})
cat(overview_html, "\n\n")
```

---

## Batter Intelligence

*Production, plate discipline, contact quality, and batted ball profile.*

```{r batter-intel-helper, include=FALSE}
# Helper: render Bootstrap pill tabs for batter intelligence tables
.render_intelligence_tabs <- function(gpk, side, uid) {
  tabs <- tryCatch(make_batter_intelligence_gt(gpk, side), error = function(e) list())
  if (length(tabs) == 0) {
    cat('<p style="color:#888; font-style:italic;">Batter intelligence data not available.</p>')
    return(invisible(NULL))
  }
  tab_names <- names(tabs)
  tab_ids   <- paste0("tab-", uid, "-", seq_along(tab_names))

  # Nav pills
  nav <- paste0(
    '<ul class="nav nav-pills" style="margin-bottom:1rem; gap:6px;" role="tablist">',
    paste(vapply(seq_along(tab_names), function(i) {
      active <- if (i == 1) ' class="nav-link active"' else ' class="nav-link"'
      paste0('<li class="nav-item"><a', active,
             ' id="', tab_ids[i], '-tab"',
             ' data-bs-toggle="pill" href="#', tab_ids[i], '" role="tab">',
             tab_names[i], '</a></li>')
    }, character(1)), collapse = ""),
    '</ul>'
  )

  # Tab content
  content <- paste0(
    '<div class="tab-content">',
    paste(vapply(seq_along(tab_names), function(i) {
      active_cls <- if (i == 1) "show active" else ""
      paste0('<div class="tab-pane fade ', active_cls,
             '" id="', tab_ids[i], '" role="tabpanel">',
             gt::as_raw_html(tabs[[i]]),
             '</div>')
    }, character(1)), collapse = ""),
    '</div>'
  )

  cat(nav, content, sep = "\n")
}
```

### `r away_team`

```{r batter-intel-away}
#| output: asis
.render_intelligence_tabs(gpk, "away", "away")
```

### `r home_team`

```{r batter-intel-home}
#| output: asis
.render_intelligence_tabs(gpk, "home", "home")
```

---

## vs Tonight's Arsenal

*Run value per 100 pitches faced — positive = above average vs that pitch type.*

### `r away_team` batters vs `r home_sp_name`

```{r pitch-vuln-away}
#| output: asis
vuln_away <- tryCatch(make_pitch_vulnerability_gt(gpk, "away"), error = function(e) {
  dplyr::tibble(Note = paste0("Unavailable: ", conditionMessage(e))) %>%
    gt::gt() %>%
    gt::tab_header(title = paste0(away_team, " vs Tonight's Arsenal")) %>%
    gt::tab_options(table.font.size = 12, heading.align = "left",
                    data_row.padding = gt::px(4)) %>%
    gt::opt_stylize(style = 1, color = "blue")
})
cat(gt::as_raw_html(vuln_away), "\n\n")
```

### `r home_team` batters vs `r away_sp_name`

```{r pitch-vuln-home}
#| output: asis
vuln_home <- tryCatch(make_pitch_vulnerability_gt(gpk, "home"), error = function(e) {
  dplyr::tibble(Note = paste0("Unavailable: ", conditionMessage(e))) %>%
    gt::gt() %>%
    gt::tab_header(title = paste0(home_team, " vs Tonight's Arsenal")) %>%
    gt::tab_options(table.font.size = 12, heading.align = "left",
                    data_row.padding = gt::px(4)) %>%
    gt::opt_stylize(style = 1, color = "blue")
})
cat(gt::as_raw_html(vuln_home), "\n\n")
```

---

## Sustainability

*Expected stats (Statcast xBA, xwOBA) vs actual performance — identifies over/underperformers.*

### `r away_team`

```{r sustainability-away}
#| output: asis
sust_away <- tryCatch(make_sustainability_gt(gpk, "away"), error = function(e) NULL)
if (!is.null(sust_away)) {
  cat(gt::as_raw_html(sust_away))
} else {
  cat(paste0('*Sustainability data not available for ', away_team, '.*\n\n'))
}
```

### `r home_team`

```{r sustainability-home}
#| output: asis
sust_home <- tryCatch(make_sustainability_gt(gpk, "home"), error = function(e) NULL)
if (!is.null(sust_home)) {
  cat(gt::as_raw_html(sust_home))
} else {
  cat(paste0('*Sustainability data not available for ', home_team, '.*\n\n'))
}
```

---

## Baserunning

*Speed, stolen base efficiency, and extra-base advancement value.*

### `r away_team`

```{r baserunning-away}
#| output: asis
br_away <- tryCatch(make_baserunning_gt(gpk, "away"), error = function(e) NULL)
if (!is.null(br_away)) {
  cat(gt::as_raw_html(br_away))
} else {
  cat(paste0('*Baserunning data not available for ', away_team, '.*\n\n'))
}
```

### `r home_team`

```{r baserunning-home}
#| output: asis
br_home <- tryCatch(make_baserunning_gt(gpk, "home"), error = function(e) NULL)
if (!is.null(br_home)) {
  cat(gt::as_raw_html(br_home))
} else {
  cat(paste0('*Baserunning data not available for ', home_team, '.*\n\n'))
}
```
