---
title: "Game Deep Dive"
date: today
params:
  game_pk: null
  game_date: null
format:
  html:
    self-contained: true
    embed-resources: true
    theme: cosmo
    toc: true
    toc-depth: 3
    toc-title: "Sections"
    toc-location: left
    smooth-scroll: true
execute:
  echo: false
  warning: false
  message: false
---

```{=html}
<style>
/*
 * Lineup stat panels: tabs on mobile, all panels side-by-side on desktop.
 * Breakpoint 1100px — roughly when a laptop has enough horizontal room.
 */
@media (min-width: 1100px) {
  .lineup-desktop-all .nav-tabs {
    display: none !important;
  }
  .lineup-desktop-all .tab-content {
    display: flex;
    gap: 14px;
    align-items: flex-start;
  }
  .lineup-desktop-all .tab-pane {
    display: block   !important;
    opacity: 1       !important;
    visibility: visible !important;
    padding-top: 0   !important;
    flex: 1 1 0;
    min-width: 0;
    overflow-x: auto;  /* each panel scrolls independently if needed */
  }
}
</style>
```

```{r setup}
#| output: false
if (basename(getwd()) == "09_reporting") setwd("..")

library(gt)
library(dplyr)
library(stringr)

# Load from pipeline cache written by render_report.R (fast path).
# Falls back to running the full pipeline if cache is missing or stale.
cache_path <- "data/pipeline_cache.rds"
cache_ok   <- file.exists(cache_path) &&
              difftime(Sys.time(), file.mtime(cache_path), units = "hours") < 12

if (cache_ok) {
  cache <- readRDS(cache_path)
  list2env(cache, envir = .GlobalEnv)
  rm(cache)
} else {
  invisible(capture.output(source("run_pipeline_phase01.R")))
}

source("09_reporting/_report_helpers.R")
source("09_reporting/_deepdive_helpers.R")
source("09_reporting/_game_narrative_helpers.R")

# Scope to this game
gpk  <- as.integer(params$game_pk)
game <- game_context %>% dplyr::filter(game_pk == gpk)

away_team <- game$away_team_name
home_team <- game$home_team_name
matchup   <- sprintf("%s @ %s", away_team, home_team)
```

```{r header}
#| output: asis
cat(sprintf("# %s\n\n", matchup))

stats_season <- if (exists("offense_master_season") && nrow(offense_master_season) > 0)
  unique(offense_master_season$season)[1] else "—"

cat(paste0(
  "> **", format(as.Date(params$game_date), "%A, %B %d, %Y"), "**",
  " · ", game$venue_name,
  " · ", stats_season, " season stats\n\n"
))
```

```{r nav-bar}
#| output: asis
scouting_file <- paste0("scouting_", params$game_date, ".html")

away_abbr_str <- tryCatch({
  team_ids %>% dplyr::filter(mlbam_team_id == game$away_team_id) %>%
    dplyr::pull(team_abbr) %>% dplyr::first()
}, error = function(e) "AWAY")

home_abbr_str <- tryCatch({
  team_ids %>% dplyr::filter(mlbam_team_id == game$home_team_id) %>%
    dplyr::pull(team_abbr) %>% dplyr::first()
}, error = function(e) "HOME")

away_abbr_str <- if (length(away_abbr_str) == 0 || is.na(away_abbr_str)) "AWAY" else away_abbr_str
home_abbr_str <- if (length(home_abbr_str) == 0 || is.na(home_abbr_str)) "HOME" else home_abbr_str

away_team_file <- paste0("team_", params$game_date, "_", away_abbr_str, ".html")
home_team_file <- paste0("team_", params$game_date, "_", home_abbr_str, ".html")

away_abbr_nav <- tryCatch({
  team_ids %>% dplyr::filter(mlbam_team_id == game$away_team_id) %>%
    dplyr::pull(team_abbr) %>% dplyr::first()
}, error = function(e) "AWAY")
home_abbr_nav <- tryCatch({
  team_ids %>% dplyr::filter(mlbam_team_id == game$home_team_id) %>%
    dplyr::pull(team_abbr) %>% dplyr::first()
}, error = function(e) "HOME")
away_abbr_nav <- if (length(away_abbr_nav) == 0 || is.na(away_abbr_nav)) "AWAY" else away_abbr_nav
home_abbr_nav <- if (length(home_abbr_nav) == 0 || is.na(home_abbr_nav)) "HOME" else home_abbr_nav

matchup_file   <- paste0("matchup_",    params$game_date, "_", away_abbr_nav, "_", home_abbr_nav, ".html")
prediction_file <- paste0("prediction_", params$game_date, "_", away_abbr_nav, "_", home_abbr_nav, ".html")
hitting_file   <- paste0("hitting_",    params$game_date, "_", away_abbr_nav, "_", home_abbr_nav, ".html")
print_file     <- paste0("print_",      params$game_date, "_", away_abbr_str,  "_", home_abbr_str,  ".html")

nav_html <- paste0(
  '<div style="margin-bottom:1.5rem; padding:10px 14px; background:#f8f9fa; ',
  'border-radius:6px; border:1px solid #dee2e6; font-size:13px;">',
  '<a href="https://dpage02.github.io/mlb_scouting_report/" style="color:#1a73e8; text-decoration:none;">',
  '\U0001f3e0 Home</a>',
  '&nbsp;&nbsp;|&nbsp;&nbsp;',
  '<a href="', scouting_file, '" style="color:#1a73e8; text-decoration:none;">',
  '\u2190 Today\'s Games</a>',
  '&nbsp;&nbsp;|&nbsp;&nbsp;',
  '<a href="', prediction_file, '" style="color:#1a73e8; text-decoration:none; font-weight:600;">',
  '\u26a1 Prediction</a>',
  '&nbsp;&nbsp;|&nbsp;&nbsp;',
  '<a href="', matchup_file, '" style="color:#1a73e8; text-decoration:none; font-weight:600;">',
  '\u26be Pitcher Matchup</a>',
  '&nbsp;&nbsp;|&nbsp;&nbsp;',
  '<a href="', hitting_file, '" style="color:#1a73e8; text-decoration:none; font-weight:600;">',
  '\u26be Hitting</a>',
  '&nbsp;&nbsp;|&nbsp;&nbsp;',
  '<a href="', away_team_file, '" style="color:#1a73e8; text-decoration:none; font-weight:600;">',
  away_team, ' Team Deep Dive \u2197</a>',
  '&nbsp;&nbsp;|&nbsp;&nbsp;',
  '<a href="', home_team_file, '" style="color:#1a73e8; text-decoration:none; font-weight:600;">',
  home_team, ' Team Deep Dive \u2197</a>',
  '&nbsp;&nbsp;|&nbsp;&nbsp;',
  '<a href="', print_file, '" style="color:#1a73e8; text-decoration:none; font-weight:600;">',
  '\U0001f5a8 Print</a>',
  '</div>'
)
cat(nav_html, "\n\n")
```

```{r game-preview}
#| output: asis
# Series overview (only shows for series openers)
series_html <- tryCatch(make_series_overview_html(gpk), error = function(e) "")
if (nchar(series_html) > 0) cat(series_html, "\n\n")

# Enhanced game narrative
narrative_html <- tryCatch(make_game_narrative_html(gpk), error = function(e) {
  tryCatch(make_game_preview_html(gpk), error = function(e2) "")
})
if (nchar(narrative_html) > 0) cat(narrative_html, "\n\n")
```

---

## Game Info

```{r game-header}
#| output: asis
cat(gt::as_raw_html(make_game_header_gt(gpk)))
```

---

## Ballpark & Conditions

```{r ballpark-conditions}
#| output: asis
bc_html <- tryCatch(make_ballpark_conditions_html(gpk), error = function(e) "")
if (nchar(bc_html) > 0) cat(bc_html, "\n\n") else
  cat('<p style="color:#888;font-style:italic;font-size:12px;">Ballpark data unavailable.</p>\n\n')
```

---

## Starting Pitchers

```{r starters}
#| output: asis
cat(gt::as_raw_html(make_starter_gt(gpk)))
cat("\n\n")
sp_splits <- make_starter_splits_gt(gpk)
if (!is.null(sp_splits)) cat(gt::as_raw_html(sp_splits))
cat("\n\n")
sp_full <- make_pitcher_full_gt(gpk)
for (nm in names(sp_full)) {
  cat(sprintf('\n\n<h4 style="margin-top:1.4rem; margin-bottom:0.3rem; color:#2c3e50;">%s</h4>\n\n', nm))
  cat(gt::as_raw_html(sp_full[[nm]]))
  cat("\n\n")
}
sp_career <- NULL  # Career history moved to team page
```

---

## Pitch Arsenal

*Pitch mix, velocity, movement, and outcomes for today's starters. Sorted by usage within each pitcher.*

```{r arsenal}
#| output: asis
arsenal_tbl <- make_arsenal_gt(gpk)
if (!is.null(arsenal_tbl)) {
  cat(gt::as_raw_html(arsenal_tbl))
} else {
  cat("*Pitch arsenal data not available for this game.*\n\n")
}
```

---

## Batter vs. Pitch Type

*How each lineup performs against the opposing starter's specific pitch mix. Run value per 100 pitches (FanGraphs) — positive = batter advantage over that pitch type.*

```{r batter-vs-pitch}
#| output: asis
bvp_html <- tryCatch(make_batter_vs_pitch_html(gpk), error = function(e) {
  paste0('<p style="color:#888; font-style:italic;">Batter vs. pitch type unavailable: ',
         conditionMessage(e), '</p>')
})
if (nchar(bvp_html) > 0) cat(bvp_html, "\n\n")
```

---

## Lineup — Analytical Breakdown

*Current season stats from MLB API, FanGraphs (all leaderboard types), and Statcast. Each section focuses on a different dimension of hitting.*

```{r lineup-full}
#| output: asis
tables_away <- make_lineup_full_gt(gpk, "away")
tables_home <- make_lineup_full_gt(gpk, "home")
away_html   <- make_lineup_tabset_html(tables_away, paste0(gpk, "away"))
home_html   <- make_lineup_tabset_html(tables_home, paste0(gpk, "home"))

.team_hdr <- function(lbl) sprintf(
  '<div style="font-size:0.95rem;font-weight:700;color:#2c3e50;margin-bottom:6px;padding-bottom:4px;border-bottom:2px solid #3498db;">%s</div>',
  lbl
)
cat(.team_hdr(away_team), away_html,
    '<div style="margin-top:2rem;"></div>',
    .team_hdr(home_team), home_html, "\n\n")
```

---

## Lineup — Matchup Splits

*Stats split by opposing starter's handedness. Shows how each batter performs against this type of pitcher.*

```{r splits-combined}
#| output: asis
away_sp <- tryCatch(starter_splits %>% dplyr::filter(game_pk == gpk, side == "away"),
                    error = function(e) data.frame())
home_sp <- tryCatch(starter_splits %>% dplyr::filter(game_pk == gpk, side == "home"),
                    error = function(e) data.frame())
away_hand <- if (nrow(away_sp) > 0 && "pitch_hand" %in% names(away_sp) &&
                  !is.na(away_sp$pitch_hand[1])) away_sp$pitch_hand[1] else "?"
home_hand <- if (nrow(home_sp) > 0 && "pitch_hand" %in% names(home_sp) &&
                  !is.na(home_sp$pitch_hand[1])) home_sp$pitch_hand[1] else "?"

splits_away_html <- gt::as_raw_html(make_lineup_splits_gt(gpk, "away"))
splits_home_html <- gt::as_raw_html(make_lineup_splits_gt(gpk, "home"))

.split_hdr <- function(team, opp_hand) sprintf(
  '<div style="font-size:0.95rem;font-weight:700;color:#2c3e50;margin-bottom:6px;padding-bottom:4px;border-bottom:2px solid #3498db;">%s \u2014 Matchup Splits <span style="font-size:0.82rem;font-weight:400;color:#666;">vs %sHP</span></div>',
  team, opp_hand
)
cat(.split_hdr(away_team, home_hand), splits_away_html,
    '<div style="margin-top:2rem;"></div>',
    .split_hdr(home_team, away_hand), splits_home_html, "\n\n")
```

---

## Lineup — Defense

*Prior season defensive metrics. Traditional (innings, errors, fielding%), Advanced (FanGraphs UZR/DRS), Statcast (OAA).*

```{r defense-combined}
#| output: asis
def_away_html <- gt::as_raw_html(make_lineup_defense_gt(gpk, "away"))
def_home_html <- gt::as_raw_html(make_lineup_defense_gt(gpk, "home"))

.team_hdr <- function(lbl) sprintf(
  '<div style="font-size:0.95rem;font-weight:700;color:#2c3e50;margin-bottom:6px;padding-bottom:4px;border-bottom:2px solid #3498db;">%s</div>',
  lbl
)
cat(.team_hdr(away_team), def_away_html,
    '<div style="margin-top:2rem;"></div>',
    .team_hdr(home_team), def_home_html, "\n\n")
```

---

## Bullpen

```{r bullpen-combined}
#| output: asis
cat('<p style="font-size:12px; margin-bottom:10px;">',
    '<span style="background:#27ae60;color:white;padding:2px 6px;border-radius:3px;">Fresh</span> &nbsp;',
    '<span style="background:#a9dfbf;color:#1a5276;padding:2px 6px;border-radius:3px;">Available</span> &nbsp;',
    '<span style="background:#f39c12;color:white;padding:2px 6px;border-radius:3px;">Limited</span> &nbsp;',
    '<span style="background:#e74c3c;color:white;padding:2px 6px;border-radius:3px;">Unavailable</span> &nbsp;',
    '<span style="background:#d5d8dc;color:#7f8c8d;padding:2px 6px;border-radius:3px;">Injured</span>',
    '</p>\n\n')
bp_away_html <- gt::as_raw_html(make_bullpen_gt(gpk, "away"))
bp_home_html <- gt::as_raw_html(make_bullpen_gt(gpk, "home"))
cat(side_by_side_html(bp_away_html, bp_home_html,
                      label1 = paste0(away_team, " Bullpen"),
                      label2 = paste0(home_team, " Bullpen")), "\n\n")
```

```{r page-links}
#| output: asis
cat(paste0(
  '<div style="margin-top:2rem; padding:14px 18px; background:#f0f4ff; ',
  'border-radius:6px; border:1px solid #c5d4f5; font-size:13px;">',
  '<strong>More analysis for this game:</strong>&nbsp;&nbsp;',
  '<a href="', matchup_file, '" style="background:#1a73e8; color:white; ',
  'padding:4px 12px; border-radius:4px; text-decoration:none; font-weight:600; margin-right:8px;">',
  '\u26be Pitcher Matchup</a>',
  '<a href="', hitting_file, '" style="background:#8e44ad; color:white; ',
  'padding:4px 12px; border-radius:4px; text-decoration:none; font-weight:600; margin-right:8px;">',
  '\u26be Hitting</a>',
  '<a href="', prediction_file, '" style="background:#27ae60; color:white; ',
  'padding:4px 12px; border-radius:4px; text-decoration:none; font-weight:600;">',
  '\u26a1 Game Prediction</a>',
  '</div>'
), "\n\n")
```
