---
title: "Full Breakdown"
date: today
page-layout: full
params:
  game_pk: null
  game_date: null
format:
  html:
    self-contained: true
    embed-resources: true
    theme: cosmo
    toc: true
    toc-depth: 3
    toc-title: "Sections"
    toc-location: left
    smooth-scroll: true
execute:
  echo: false
  warning: false
  message: false
---

```{=html}
<style>
/*
 * gt tables emit their own inline overflow-y:auto on the wrapping
 * .gt_table_container div. With height:auto that's normally a no-op, but
 * nested inside this page's flex/tab layout it can create an unwanted
 * nested vertical scroll region instead of letting the page scroll
 * normally. Same fix already applied to mlb_print.qmd for the same
 * underlying gt behavior.
 */
.gt_table_container {
  overflow-y: visible !important;
}

/*
 * Lineup stat panels: tabs on mobile, all panels side-by-side on desktop.
 * Breakpoint 1100px — roughly when a laptop has enough horizontal room.
 */
@media (min-width: 1100px) {
  .lineup-desktop-all .nav-tabs {
    display: none !important;
  }
  .lineup-desktop-all .tab-content {
    display: flex;
    gap: 14px;
    align-items: flex-start;
  }
  .lineup-desktop-all .tab-pane {
    display: block   !important;
    opacity: 1       !important;
    visibility: visible !important;
    padding-top: 0   !important;
    flex: 1 1 0;
    min-width: 0;
    overflow-x: auto;  /* each panel scrolls independently if needed */
  }
}
</style>
```

```{r setup}
#| output: false
if (basename(getwd()) == "09_reporting") setwd("..")

library(gt)
library(dplyr)
library(stringr)

# Load from pipeline cache written by render_report.R (fast path).
# Falls back to running the full pipeline if cache is missing or stale.
cache_path <- "data/pipeline_cache.rds"
cache_ok   <- file.exists(cache_path) &&
              difftime(Sys.time(), file.mtime(cache_path), units = "hours") < 12

if (cache_ok) {
  cache <- readRDS(cache_path)
  list2env(cache, envir = .GlobalEnv)
  rm(cache)
} else {
  invisible(capture.output(source("run_pipeline_phase01.R")))
}

source("09_reporting/_report_helpers.R")
source("09_reporting/_deepdive_helpers.R")
source("09_reporting/_game_narrative_helpers.R")

# Scope to this game
gpk  <- as.integer(params$game_pk)
game <- game_context %>% dplyr::filter(game_pk == gpk)

away_team <- game$away_team_name
home_team <- game$home_team_name
matchup   <- sprintf("%s @ %s", away_team, home_team)
```

```{r header}
#| output: asis
cat(sprintf("# %s — Full Breakdown\n\n", matchup))

stats_season <- if (exists("offense_master_season") && nrow(offense_master_season) > 0)
  unique(offense_master_season$season)[1] else "—"

cat(paste0(
  "> **", format(as.Date(params$game_date), "%A, %B %d, %Y"), "**",
  " · ", game$venue_name,
  " · ", stats_season, " season stats\n\n"
))
```

```{r nav-bar}
#| output: asis
scouting_file <- paste0("scouting_", params$game_date, ".html")
deepdive_file <- paste0("deepdive_", params$game_date, "_",
                        {
                          a <- tryCatch(team_ids %>% dplyr::filter(mlbam_team_id == game$away_team_id) %>%
                                          dplyr::pull(team_abbr) %>% dplyr::first(), error = function(e) "AWAY")
                          if (length(a) == 0 || is.na(a)) "AWAY" else a
                        }, "_",
                        {
                          h <- tryCatch(team_ids %>% dplyr::filter(mlbam_team_id == game$home_team_id) %>%
                                          dplyr::pull(team_abbr) %>% dplyr::first(), error = function(e) "HOME")
                          if (length(h) == 0 || is.na(h)) "HOME" else h
                        }, ".html")

away_abbr_str <- tryCatch({
  team_ids %>% dplyr::filter(mlbam_team_id == game$away_team_id) %>%
    dplyr::pull(team_abbr) %>% dplyr::first()
}, error = function(e) "AWAY")

home_abbr_str <- tryCatch({
  team_ids %>% dplyr::filter(mlbam_team_id == game$home_team_id) %>%
    dplyr::pull(team_abbr) %>% dplyr::first()
}, error = function(e) "HOME")

away_abbr_str <- if (length(away_abbr_str) == 0 || is.na(away_abbr_str)) "AWAY" else away_abbr_str
home_abbr_str <- if (length(home_abbr_str) == 0 || is.na(home_abbr_str)) "HOME" else home_abbr_str

away_team_file <- paste0("team_", params$game_date, "_", away_abbr_str, ".html")
home_team_file <- paste0("team_", params$game_date, "_", home_abbr_str, ".html")

matchup_file    <- paste0("matchup_",    params$game_date, "_", away_abbr_str, "_", home_abbr_str, ".html")
prediction_file <- paste0("prediction_", params$game_date, "_", away_abbr_str, "_", home_abbr_str, ".html")
hitting_file    <- paste0("hitting_",    params$game_date, "_", away_abbr_str, "_", home_abbr_str, ".html")
print_file      <- paste0("print_",      params$game_date, "_", away_abbr_str, "_", home_abbr_str, ".html")

nav_html <- paste0(
  '<div style="margin-bottom:1.5rem; padding:10px 14px; background:#f8f9fa; ',
  'border-radius:6px; border:1px solid #dee2e6; font-size:13px;">',
  '<a href="https://dpage02.github.io/mlb_scouting_report/" style="color:#1a73e8; text-decoration:none;">',
  '\U0001f3e0 Home</a>',
  '&nbsp;&nbsp;|&nbsp;&nbsp;',
  '<a href="', scouting_file, '" style="color:#1a73e8; text-decoration:none;">',
  '← Today\'s Games</a>',
  '&nbsp;&nbsp;|&nbsp;&nbsp;',
  '<a href="', deepdive_file, '" style="color:#1a73e8; text-decoration:none; font-weight:600;">',
  '← Game Overview</a>',
  '&nbsp;&nbsp;|&nbsp;&nbsp;',
  '<a href="', prediction_file, '" style="color:#1a73e8; text-decoration:none; font-weight:600;">',
  '⚡ Prediction</a>',
  '&nbsp;&nbsp;|&nbsp;&nbsp;',
  '<a href="', matchup_file, '" style="color:#1a73e8; text-decoration:none; font-weight:600;">',
  '⚾ Pitcher Matchup</a>',
  '&nbsp;&nbsp;|&nbsp;&nbsp;',
  '<a href="', hitting_file, '" style="color:#1a73e8; text-decoration:none; font-weight:600;">',
  '⚾ Hitting</a>',
  '&nbsp;&nbsp;|&nbsp;&nbsp;',
  '<a href="', away_team_file, '" style="color:#1a73e8; text-decoration:none; font-weight:600;">',
  away_team, ' Team Deep Dive ↗</a>',
  '&nbsp;&nbsp;|&nbsp;&nbsp;',
  '<a href="', home_team_file, '" style="color:#1a73e8; text-decoration:none; font-weight:600;">',
  home_team, ' Team Deep Dive ↗</a>',
  '&nbsp;&nbsp;|&nbsp;&nbsp;',
  '<a href="', print_file, '" style="color:#1a73e8; text-decoration:none; font-weight:600;">',
  '\U0001f5a8 Print</a>',
  '</div>'
)
cat(nav_html, "\n\n")
```

*4-pillar tabset (Master Build Spec §3). This slice fully builds out
the **Lineup → Offense** sub-tab for both teams; Pitching, Team Context, Matchups,
and the Baserunning/Defense/Catcher sub-tabs are placeholders pending the next
slices.*

```{r offense-tab-helper, include=FALSE}
# Two independent pandoc/CommonMark quirks corrupt fenced-div (panel-tabset)
# parsing when a gt table is emitted inside one, unless both are fixed:
# 1. gt::as_raw_html() sometimes emits TWO consecutive whitespace-only lines
#    (e.g. around an empty tfoot). A blank line inside a raw HTML block ends
#    it early under CommonMark's rules; {2,} collapses runs of any length,
#    not just one (a single-pass regex only catching one blank line at a
#    time misses runs of 2+, since gsub doesn't backtrack/overlap matches).
# 2. gt emits bare `<col style="...">` tags (HTML void elements) for column
#    widths. Pandoc's block-tag matcher doesn't recognize <col> as
#    self-closing and treats it as an unterminated open tag, silently
#    swallowing everything through EOF into one Div (including this
#    tabset's own closing ':::', which then leaks into the page as literal
#    text). Self-closing the tag (`<col ... />`) fixes it.
# Shared across all Lineup sub-tabs (Offense/Baserunning/Defense/Catcher).
.gt_html <- function(tbl) {
  html <- gt::as_raw_html(tbl)
  html <- gsub("(\n[ \t]*){2,}", "\n", html)
  gsub("<col([^>]*)>", "<col\\1 />", html)
}

# Combines Batter Intelligence (Overview / Discipline & Contact / Batted Ball),
# Sustainability, and Clutch+Platoon into one Offense sub-tab, stacked as a
# narrative sequence (approach -> contact -> quality -> deserved outcomes ->
# clutch -> platoon) rather than further nested tabs.
.render_offense_tab <- function(gpk, side) {
  sub_hdr <- function(txt) sprintf(
    '<div style="font-size:0.85rem;font-weight:700;color:#2c3e50;margin:1.1rem 0 0.4rem 0;text-transform:uppercase;letter-spacing:0.02em;">%s</div>',
    txt
  )

  bi <- tryCatch(make_batter_intelligence_gt(gpk, side), error = function(e) list())
  if (length(bi) > 0) {
    cat(sub_hdr("Production &amp; Approach"), "\n\n")
    cat(.gt_html(bi[["Overview"]]), "\n\n")
    cat(sub_hdr("Plate Discipline, Contact &amp; Quality of Contact"), "\n\n")
    cat(.gt_html(bi[["Discipline & Contact"]]), "\n\n")
    cat(sub_hdr("Batted Ball Profile"), "\n\n")
    cat(.gt_html(bi[["Batted Ball & Profile"]]), "\n\n")
  } else {
    cat('<p style="color:#888;font-style:italic;">Batter intelligence data not available.</p>\n\n')
  }

  sust <- tryCatch(make_sustainability_gt(gpk, side), error = function(e) NULL)
  if (!is.null(sust)) {
    cat(sub_hdr("Deserved Outcomes (Sustainability)"), "\n\n")
    cat(.gt_html(sust), "\n\n")
  }

  cp <- tryCatch(make_offense_clutch_platoon_gt(gpk, side), error = function(e) list())
  if (length(cp) > 0) {
    cat(sub_hdr("Clutch / Leverage"), "\n\n")
    cat(.gt_html(cp[["Clutch / Leverage"]]), "\n\n")
    cat(sub_hdr("Handedness Split (Season-Long)"), "\n\n")
    cat(.gt_html(cp[["Handedness Split"]]), "\n\n")
  }
}

.render_baserunning_tab <- function(gpk, side) {
  tbl <- tryCatch(make_baserunning_gt(gpk, side), error = function(e) NULL)
  if (!is.null(tbl)) cat(.gt_html(tbl), "\n\n")
  else cat('<p style="color:#888;font-style:italic;">Baserunning data not available.</p>\n\n')
}

.render_defense_tab <- function(gpk, side) {
  tbl <- tryCatch(make_lineup_defense_gt(gpk, side), error = function(e) NULL)
  if (!is.null(tbl)) cat(.gt_html(tbl), "\n\n")
  else cat('<p style="color:#888;font-style:italic;">Defense data not available.</p>\n\n')
}

# Position-gated: only emits content (and thus only becomes a meaningful
# tab) when this team's lineup has a catcher; make_catcher_defense_gt
# returns NULL otherwise.
.render_catcher_tab <- function(gpk, side) {
  tbl <- tryCatch(make_catcher_defense_gt(gpk, side), error = function(e) NULL)
  if (!is.null(tbl)) cat(.gt_html(tbl), "\n\n")
  else cat('<p style="color:#888;font-style:italic;">No catcher in this lineup.</p>\n\n')
}
```

::: {.panel-tabset}

### Pitching

*Coming soon — will absorb the Starting Pitchers and Pitch Arsenal sections below.*

### Lineup

::: {.panel-tabset}

### `r away_team`

::: {.panel-tabset}

### Offense

```{r offense-away}
#| output: asis
.render_offense_tab(gpk, "away")
```

### Baserunning

```{r baserunning-away}
#| output: asis
.render_baserunning_tab(gpk, "away")
```

### Defense

```{r defense-away}
#| output: asis
.render_defense_tab(gpk, "away")
```

### Catcher

```{r catcher-away}
#| output: asis
.render_catcher_tab(gpk, "away")
```

:::

### `r home_team`

::: {.panel-tabset}

### Offense

```{r offense-home}
#| output: asis
.render_offense_tab(gpk, "home")
```

### Baserunning

```{r baserunning-home}
#| output: asis
.render_baserunning_tab(gpk, "home")
```

### Defense

```{r defense-home}
#| output: asis
.render_defense_tab(gpk, "home")
```

### Catcher

```{r catcher-home}
#| output: asis
.render_catcher_tab(gpk, "home")
```

:::

:::

### Team Context

*Coming soon — standings, park factors, weather (Master Build Spec §3, View 3).*

### Matchups

*Coming soon — starter's last 3 starts, batter vs. pitcher, baserunning matchup
(Master Build Spec §3, View 4).*

:::
